---
title: "Airline Satisfaction"
author: 
  - Marc Parcerisa
  - Albert Puiggròs
  - Dani Reverter
output:
    pdf_document: default
    html_document: default
    md_document: 
      variant: markdown_github
editor_options:
  chunk_output_type: console
---

<!-- README.md is generated from AirlineSatisfaction.Rmd. Please edit that file. --> 

This project aims to predict airline passenger satisfaction levels by developing
and analyzing binary regression models. Using a dataset containing customer
demographics, flight details, and satisfaction ratings for various services, the
project explores key factors influencing satisfaction. The workflow encompasses
comprehensive data preparation, including cleaning, transformation, and
profiling, followed by exploratory data analysis and model building.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "images/")
```

```{r, include=FALSE}
# Load libraries
library(FactoMineR)
library(cluster)
library(missMDA)
```

# Data preparation

Data preparation will be broken down into two main steps. The first step 
involves transforming the data into a usable format, converting factors into 
such and removing useless columns, and will be applied to both training and
testing datasets. The second one will focus on cleaning the data, removing
missing values, and outliers, and will be applied only to the training dataset.

## Data transformation

We'll start by defining a new function that will perform the first step of data
preparation. This function will remove the "X" and "id" columns, and convert
most of the columns to factors.

```{r}
prepareDataset <- function(data) {
  "Prepare dataset for analysis"
  # Remove useless columns "X" and "id"
  data$X <- NULL
  data$id <- NULL

  # Convert columns to factors
  data$Gender <- as.factor(data$Gender)
  data$Customer.Type <- as.factor(data$Customer.Type)
  data$Type.of.Travel <- as.factor(data$Type.of.Travel)
  data$Class <- factor(data$Class, levels = c("Eco", "Eco Plus", "Business"), ordered = TRUE)

  stais_cols <- c(
    "Inflight.wifi.service", "Departure.Arrival.time.convenient",
    "Ease.of.Online.booking", "Gate.location", "Food.and.drink",
    "Online.boarding", "Seat.comfort", "Inflight.entertainment",
    "On.board.service", "Leg.room.service", "Baggage.handling",
    "Checkin.service", "Inflight.service", "Cleanliness"
  )
  for (col in stais_cols) {
    data[[col]] <- factor(data[[col]], levels = 0:5, ordered = TRUE)
  }

  data$satisfaction <- as.factor(data$satisfaction)
  return(data)
}
```

Now we'll load the training and testing datasets and apply the `prepareDataset`
function to both.

```{r}
# Load datasets
train <- read.csv("data/train_data.csv")
test <- read.csv("data/test_data.csv")

# Prepare datasets
train <- prepareDataset(train)
test <- prepareDataset(test)
```

Let's take a look at the first few rows of the training dataset to ensure that
the transformation was successful.

```{r}
str(train)
```

## Data cleaning

This next step will focus on cleaning the training dataset. We'll start by 
removing duplicate rows, counting and imputing missing values.

```{r}
# Find duplicate rows
duplicates <- train[duplicated(train), ]
cat("Number of duplicate rows:", nrow(duplicates), "\n")
```

```{r, include=FALSE}
rm(duplicates)
gc()
```

We found no duplicates. Let's now count the missing values in each column.

```{r}
# Count missing values
missing_values <- colSums(is.na(train))
for (col in names(missing_values)) {
  if (missing_values[col] > 0) {
    cat("Column", col, "has", missing_values[col], "missing values\n")
  }
}
```

There's 12 missing values in the "Arrival.Delay.in.Minutes" column. As most of
our columns are factors, we would impute them using Multiple Correspondence
Analysis (MCA). However, the dataset at hand is too large for this method to be
feasible. Instead, seeing as the number of missing values is small, we'll
simply remove the rows with missing values.

```{r}
# Remove rows with missing values
before <- nrow(train)
train <- train[complete.cases(train), ]
after <- nrow(train)
cat("Removed", before - after, "rows with missing values\n")
```

```{r, include=FALSE}
rm(before, after, missing_values)
gc()
```

Now that we've removed the rows with missing values, let's check for outliers in
the numerical columns.

```{r}
# Check for outliers
numeric_df <- Filter(is.numeric, train)
# There's 4 numerical columns
par(mfrow = c(2, 2))
for (col in names(numeric_df)) {
  boxplot(numeric_df[[col]], main = col, horizontal = TRUE)

  # Calculate IQR
  q1 <- quantile(numeric_df[[col]], 0.25)
  q3 <- quantile(numeric_df[[col]], 0.75)
  iqr <- q3 - q1

  # Add the lines to the plot
  abline(v = c(q1 - 1.5 * iqr, q3 + 1.5 * iqr), col = "orange")
  abline(v = c(q1 - 3 * iqr, q3 + 3 * iqr), col = "red")

  # Find outliers
  mild_outliers <- which(
    numeric_df[[col]] < (q1 - 1.5 * iqr) & numeric_df[[col]] > (q1 - 3 * iqr) |
      numeric_df[[col]] > (q3 + 1.5 * iqr) & numeric_df[[col]] < (q3 + 3 * iqr)
  )
  severe_outliers <- which(numeric_df[[col]] < (q1 - 3 * iqr) | numeric_df[[col]] > (q3 + 3 * iqr))


  cat("Column", col, "has", length(mild_outliers), "mild outliers and", length(severe_outliers), "severe outliers\n")
}
```

```{r, include=FALSE}
rm(numeric_df, q1, q3, iqr, mild_outliers, severe_outliers, col)
gc()
```

Looking at the boxplots, we can see that there are no severe outliers in neither
"Age" nor "Flight.Distance", but there are some in "Departure.Delay.in.Minutes"
and "Arrival.Delay.in.Minutes". However, none of them look too extreme to be
considered errors. Moreover, knowing as we aim to predict satisfaction, arguably
the more extreme the delays are, the more likely the passenger is to be
dissatisfied, providing valuable modeling information. Therefore, we'll keep
them as they are.

Instead, knowing that the arrival and departure delays must be strongly 
correlated, we'll plot them to check if any anomalies are present, indicating
errors in the data.

```{r}
# Plot departure vs arrival delays
par(mfrow = c(1, 1))
plot(train$Departure.Delay.in.Minutes, train$Arrival.Delay.in.Minutes, xlab = "Departure Delay (min)", ylab = "Arrival Delay (min)")
abline(a = 0, b = 1, col = "red")
```

No points seem to be too far from the red line, so we'll consider them as valid
data points.

Before proceeding, we must note that there is a slight imbalance in the target 
variable "Satisfaction", which could affect the model's performance. We'll
address this issue in later sections.

```{r}
table(train$satisfaction)
```



